\documentclass[twocolumn]{aastex62}

% \submitjournal{ApJ}

\shortauthors{Beane et al.}

\usepackage{graphicx}

\newcommand{\Gus}[1]{\textcolor{red}{#1}}

\newcommand{\Msun}{\text{M}_\odot}
\newcommand{\pc}{\text{pc}}
\newcommand{\kpc}{\text{kpc}}

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\z}{z}

\newcommand{\mi}{\texttt{m12i}}
\newcommand{\mf}{\texttt{m12f}}
\newcommand{\mm}{\texttt{m12m}}

\begin{document}

\title{The Actions We Compute are Not Invariant}

\correspondingauthor{Angus Beane}
\email{abeane@sas.upenn.edu}

\author{Angus Beane}
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 5th
Ave., New York, NY 10010, USA}
\affil{Department of Physics \& Astronomy, University of Pennsylvania, 209
South 33rd St., Philadelphia, PA 19104, USA}

\author{Many Helpful People}
\noaffiliation

\begin{abstract}

In an axisymmetric potential the 6D phase space of stars' positions and
velocities can be reduced to a 3D space of invariant actions. For this reason
actions are commonly used to help interpret phase space. We show that if one
assumes the wrong galactocentric reference frame this can induce artificial
non-axisymmetries which manifest as time dependence in the computed actions.
However, the Milky Way is not axisymmetric in detail and so there are no
truly axisymmetric axes. We instead define the  ``optimally axisymmetric''
axes as the reference frame which minimizes the time dependence of the
actions. Using cosmological zoom-in simulations from FIRE-2, we show that the
optimally axisymmetric reference frame can differ from standard methods of
calculating the galactocentric reference frame by (some numbers). We further
show that if one uses the conventional method to define the Galactic midplane
in this simulated galaxy, the midplane can vary by nearly a scale height
across the galaxy. This work calls into question the use of actions as
dynamical invariants unless these reference frame issues can be resolved.

% However, it is not expected that actions are invariant in detail for the
% Milky Way. This in-invariance can come about from assuming the wrong
% Galactic potential, but it can also come about due to true
% non-axisymmetries. We show that actions can gain artificial time-dependence
% also by assuming the wrong reference frame. We argue that standard methods
% for determining the galactocentric reference frame are not gu

% it's spiral arms, bar(s), and gas clouds are all non-axisymmetric features
% that should induce long-term evolution in action space. However, these same
% features will cause a star's true orbit to deviate slightly from its orbit
% in an axisymmetric potential. If an observer assumes an axisymmetric
% potential when computing actions, this will induce an artificial short-term
% phase dependence of the actions, which we interpret as systematic error.
% Using the potential of cosmological zoom-in simulations of Milky Way mass
% galaxies from the FIRE collaboration (the Latte suite), we investigate the
% magnitude of this systematic error. We find XXX. Something something lower
% limit.

\end{abstract}

\keywords{actions}

\section{Introduction} \label{sec:intro}


Midplane resolved with $\sim 370$ to $570$ star particles.

We could have proceeded by taking an axisymmetric potential and adding
analytic spiral arms, a bar, and gas clouds. However, in preliminary work
with the FIRE galaxies we found that defining a consistent reference frame
between snapshots was very difficult. An inaccuracy in the direction of the
$z$-axis by a single degree induces a $140\,\pc$ change in the height of the
midplane at $8.2\,\kpc$. In a cosmological context it is not apparent that
there exists a consistent definition of the galactocentric frame, and we
therefore proceed in a cosmological context to include this effect.

We perform a set of three different simulations repeated for two of the Milky
Way zoom-ins, \mi and \mf.\footnote{The number corresponds to the mass of the
dark matter halo (here, $\sim 10^{12} \Msun$). The first ``m'' stands for
mass and the last letter is a unique identifier for the {\em initial
conditions}.} The first assumes an axisymmetric potential and also implicitly
a well-defined galactocentric frame. This first simulation shows that our
integration technique respects the fact that in an axisymmetric potential
actions are invariant and that our calculation of the actions does not
imprint some artificial phase dependence in the actions.


\section{Methods} \label{sec:methods}
We begin by 

Rockstar import in gizmo\_analysis is commented out

\subsection{Simulated Galaxies} \label{ssec:fire}
We wish to perform N-body integration within a realistic Galactic potential.
In order to do this, we use the {\em Latte} suite of Milky Way-mass zoom-ins
from the Feedback in Realistic Environments (FIRE)
collaboration\footnote{\url{http://fire.northwestern.edu}}
\citep{2016ApJ...827L..23W,2018MNRAS.480..800H}. In a zoom-in cosmological
simulation a high resolution region of interest is embedded within a low
resolution cosmological context (\Gus{cites}). In the case of {\em Latte}, a
region that will evolve into a Milky Way-mass galaxy, identified in a
preliminary dark matter only run, is increased in resolution using MUSIC.
This allows one to achieve ultra-high resolution simulations of individual
galaxies than possible in a full cosmological run. 



Our centering differs from Sanderson et al. by $\sim3.2\,\pc$ for \mi.


\section{Optimally Axisymmetric Frame}
An analytic, axisymmetric potential with a known reference frame is a far too
simple description of the Milky Way. We thus turn to cosmological zoom-in
simulations as approximations to a ``true'' Milky Way potential. We will perform a few simulations of small clusters in order to 

\subsection{Cosmological Zoom-in} \label{ssec:cosmozoom}
Cosmological zoom-ins allow one to simulate a selected region at high
resolution embedded in a low-resolution cosmological background
\citep[e.g.][]{1993ApJ...412..455K,2014MNRAS.437.1894O}. Here we use a
zoom-in of a Milky Way-mass galaxy from the FIRE-2 collaboration.

First, a dark matter only simulation was run with $\Lambda$CDM cosmology
parameterized by $(\Omega_m, \Omega_{\Lambda}, \Omega_b, h, \sigma_8, n_s) =
(0.272, 0.728, 0.0455, 0.702, 0.807, 0.961)$, consistent with current
constraints \citep{2018arXiv180706209P}. Halos are selected at $z=0$ based
solely on their mass ($\sim 1\text{--}2 \times 10^{12} \Msun$). Particles
within $5 R_{200\text{m}}$ of each halo are traced back to $\z=99$ and the
initial conditions are regenerated at higher resolution using MUSIC
\citep{2011MNRAS.415.2101H}. A total of $\sim 10$ halos were simulated at
higher resolution \citep{2018MNRAS.481.4133G}.

These halos are uncontaminated and contain gas particles of mass $\sim 7000
\text{--} 20000 \Msun$ and star particles of mass $\sim 5000 \text{--} 7000
\Msun$, with the lower end coming from stellar evolution
\citep{2018arXiv180610564S}. Softening lengths for dark matter and star
particles are fixed at $112\,\pc$ and $11.2\,\pc$,
respectively.\footnote{This is $2.8$ times the often-quoted
Plummer-equivalent.} The gas softening length is adaptive, but at $z=0$ the
median softening length for gas particles around roughly solar positions
(with cylindrical radii within $500\,\pc$ of $8.2\,\kpc$ and
$\abs{z}<1\,\kpc$) is $98\,\pc$.

We restrict ourselves to the simulation \texttt{m12i} \citep[first introduced
in][]{2016ApJ...827L..23W}. For this work, this galaxy is the best-case
scenario. It does not contain a bar (like \texttt{m12m}) or companion galaxy,
and by eye is the closest to axisymmetric of the three galaxies presented in
\citet{2018arXiv180610564S} \citep{2018MNRAS.481.4133G}.

It is important to remember that simulations of Milky Way-mass galaxies are
not perfect representations of the true Milky Way, as discussed in
\citet{2018arXiv180610564S}. For instance, the velocity structure of
\texttt{m12i} is closer to M31 than the Milky Way. However, in this work we
are most interested in the global properties of the \texttt{m12i} potential,
and specifically in deviations from axisymmetry. From this perspective,
\texttt{m12i} is actually far more axisymmetric than we might expect of the
Milky Way. While \texttt{m12i} has prominent spiral arms, it lacks a bar and
a companion like the Large Magellanic Cloud. In future work, these additional
complications also need to be addressed.

\subsection{Cluster Simulations} \label{ssec:cluster_sim}
We simulate a small star cluster of $256$ stars in the frozen $\z=0$
potential of $\texttt{m12i}$. We use the code \texttt{ph4} within the
\texttt{AMUSE} framework \citep{2011ascl.soft07007P, 2013CoPhC.184..456P,
2013A&A...557A..84P} for the cluster integration. We use a softening length
of $0.01\,\pc$ which means we do not correctly solve the internal dynamics of
the cluster, but this is not important for our purposes. To couple the
gravitational forces of the frozen snapshot to the cluster stars, we use the
\texttt{BRIDGE} \citep{2007PASJ...59.1095F}, also implemented in
\texttt{AMUSE}. Our simulation runs for $2\,\Gyr$, allowing us to solve for
$\sim 10$ orbits.

To compute the forces from the frozen potential, we use the simple tree code
\texttt{pykdgrav}\footnote{\url{https://github.com/omgspace/pykdgrav},
commit:\texttt{fbd1ddc}}. 

We use the initial position and velocity of two star particles in
$\texttt{m12i}$

\appendix \section{Appendix 1}
Gonna write an appendix probably 

\bibliography{references}

\end{document}
